BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-14 tex/5-evaluation.tex
Up

In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}.

As presented in section \autoref{techniques}, our crawler uses a full web browser to render pages.

To achieve this property, our final solution was to embed a full web browser into our system, , which we use to take screen-shots of pages. Before choosing this tool we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.

>>>>

In addition to the extraction of blog content that we have been discussing so far, the BlogForever crawler is also responsible for capturing blog visuals. Indeed, one of the requirements of the BlogForever platform is to provide snapshots of blogs visuals in order to preserve changes in appearance \cite[FR53]{blogforeverrequirements2009}. As presented in section \autoref{techniques}, our crawler embed a full web browser in the harvesting process. In addition (***rep) to the JavaScript rendering, the browser also take care of visu by screenschots

in order to support blogs that use JavaScript to download and display content.

*dis also takes case of screenshots*. Before opting for this we considered 3 other solutions: wget, wkhtmltopdf, oxpath. This subsection relates our evaluation of these tools for the specific purpose.
